Model-based pretreatment for regression with correlated variables.

### 2014-04-08 www/article13.tex
updated formalism
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@509 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

	We note $\boldsymbol{\Theta}$ the set of the parameters of the generative model
	\begin{eqnarray}
		P(S|\boldsymbol{X})&\propto& P(\boldsymbol{X}|S)P(S) \label{approxBIC}\\
		-2\log P(\boldsymbol{X}|S)&\approx & BIC=-2\mathcal{L}(\boldsymbol{X},S,\boldsymbol{\Theta})+|\boldsymbol{\Theta}|\log(n)  
	\end{eqnarray}
	But $BIC$ tends to give too complex structures because we test a great range of models. 
	Thus we choose to penalise the complexity a bit more with a hierarchical uniform {\it a priori} law $P(S)=P(I_1 | p_1,I_2,p_2)P(p_1|I_2,p_2)P(I_2|p_2)P(p_2)$  instead of a simple uniform law on $S$.
%	 Thus we have :
%		\begin{eqnarray}
%		BIC^*(X|S)&=&BIC(X|S) +\ln(P(S)) \label{Bicstar}
%	\end{eqnarray}		
	It increases penalty on complexity for $p_2<\frac{p}{2}$ and $p_1^j<\frac{p}{2}$ . Hence %when using $BIC*$ 
	this constraint on $\hat{p}_2$ and $\hat{p}_1^j$ is made in the MCMC in the followings.
		We do not change $BIC$ but only $P(S)$ so the properties are the same as classical $BIC$ but we will obtain better results when our hypothesis is verified.

@@

\clearpage
\subsection{Results on prediction}
	\subsubsection{$Y$ depends on all variables in $X$}	 \label{tableMSEsimtout}	
We first try the method with a response depending on all covariates (\textsc{CorReg} reduces the dimension and can't give the true model if there is a structure). The datasets used here were those from table \ref{compZvrai}.

@@

$n$ & $p_2$& $\psi$ & indicator &OLS  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 

@@

\caption{OLS and OLS combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X$. \textsc{CorReg} logically wins. When $n<p$ the dataset was reduced to $p=n$ automatically by a $QR$ decomposition as the lm function of R does. Without selection, all models have min$(n,p)$ non-zero coefficients.} \label{YXlinOLS}

@@

$n$ & $p_2$&  $\psi$ &indicator &LASSO  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 

@@

\caption{LASSO (with LAR) combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X$. \textsc{CorReg} logically wins. LASSO is better than OLS but is improved by \textsc{CorReg} even for large values of $n$.}\label{YXlinLASSO}

@@

$n$ & $p_2$&  $\psi$ &indicator &Elasticnet  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 

@@

\caption{Elasticnet combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X$. \textsc{CorReg} logically wins. LASSO was better.}\label{YXlinenet}

@@

$n$ & $p_2$&  $\psi$ &indicator &Stepwise  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 

@@

\caption{Stepwise  combined with constrained \textsc{CorReg}. $Y$ depends on all variables in $X$. \textsc{CorReg} logically wins but stepwise is quite good compared to elasticnet.}\label{YXlinstep}

@@

\clearpage
	\subsubsection{$Y$ depends only on covariates in $X_2$ (worst case for us)}	 \label{tableMSEsimgauche}
We now try the method with a response depending only on variables in $X_2$. The datasets used here were still those from \ref{compZvrai}.
Depending only on $X_2$ imply sparsity and impossibility to obtain the true model when using the true structure. \textsc{CorReg} is still better than classical methods.

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $\psi$ &indicator &OLS  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 81781.54 (247281.7) & 507.1 (269.2) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.11 (1) & 25 (0) \\
 &  &HU &MSE (sd) & 81781.54 (247281.7) & 587.07 (425.6) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.82 (0.6) & 25 (0) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 74136.81 (297716.1) & 189.45 (48.1) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 13.85 (0.9) & 9 (0) \\
 &  & HU & MSE (sd) & 74136.81 (297716.1) & 340.53 (169.4) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 21 (0) & 9 (0) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 684.04 (438.1) & 190.97 (37.7) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.43 (0.7) & 25 (0) \\
 &  &HU &MSE (sd) & 684.04 (438.1) & 196.36 (40.5) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.99 (0.5) & 25 (0) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 596.32 (323) & 126.94 (15.5) & 119.39 (12.4) \\
& & & cpl (sd) & 41 (0) & 11.45 (0.9) & 9 (0) \\
 &  &HU &MSE (sd) & 596.32 (323) & 168.03 (27.7) & 119.39 (12.4) \\
& & &cpl (sd) & 41 (0) & 21 (0) & 9 (0) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U&  MSE (sd) & 168.35 (20.1) & 133.75 (12.4) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 24.53 (0.7) & 25 (0) \\
 &  &HU &  MSE (sd) & 168.35 (20.1) & 135.04 (13.1) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 25.01 (0.4) & 25 (0) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U&  MSE (sd) & 168.07 (21.4) & 109.61 (7.4) & 108.64 (7.2) \\
& & &  cpl (sd) & 41 (0) & 10.02 (0.8) & 9 (0) \\
 &  &HU & MSE (sd) & 168.07 (21.4) & 124.23 (11.1) & 108.64 (7.2) \\
& & & cpl (sd) & 41 (0) & 21 (0) & 9 (0) \\
\hline
\end{tabular} 
\caption{OLS and OLS combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X_2$. Sometimes $\hat{S}$ gives better results than $S$ because $S$ is penalized by the fact that it relies only on covariates not in the true model. } \label{YX2linOLS}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $\psi$ &indicator &LAR  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 367.45 (198.4) & 298.32 (122.4) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.9 (3.8) & 12.84 (3.8) \\
 &  &HU &MSE (sd) & 367.45 (198.4) & 298.1 (119.1) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.81 (3.8) & 12.84 (3.8) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 273.12 (267.2) & 166.93 (49) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 8.7 (2.5) & 7.45 (1.4) \\
 &  & HU & MSE (sd) & 273.12 (267.2) & 175.68 (57.5) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 9.19 (2.9) & 7.45 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 189.64 (52.5) & 171.97 (45.9) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.4 (2.8) & 13.5 (3.1) \\
 &  &HU &MSE (sd) & 189.64 (52.5) & 174.36 (45.3) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.57 (3) & 13.5 (3.1) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 163.88 (67.4) & 124.53 (17) & 121.99 (16.6) \\
& & & cpl (sd) & 13.06 (7.2) & 8.29 (1.6) & 7.73 (1.2) \\
 &  &HU &MSE (sd) & 163.88 (67.4) & 133.7 (26.4) & 121.99 (16.6) \\
& & &cpl (sd) & 13.06 (7.2) & 9.65 (3.3) & 7.73 (1.2) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U& MSE (sd) & 129.65 (14.8) & 127.11 (12.1) & 127.46 (12.2) \\
& & &  cpl (sd) & 14.86 (3.1) & 13.97 (2.5) & 14.04 (2.5) \\
 &  &HU &  MSE (sd) & 129.65 (14.8) & 127.46 (12.2) & 127.46 (12.2) \\
& & & cpl (sd) & 14.86 (3.1) & 14.02 (2.5) & 14.04 (2.5) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U&  MSE (sd) & 121.21 (20.1) & 109.66 (7.9) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 8.42 (1.1) & 8.11 (0.8) \\
 &  &HU &  MSE (sd) & 121.21 (20.1) & 112.56 (11.2) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 9.77 (2.3) & 8.11 (0.8) \\
\hline
\end{tabular} 
\caption{LASSO (with LAR) combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X_2$. }\label{YX2linLASSO}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $\psi$ &indicator & Elasticnet  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 499.32 (218.8) & 311.41 (137.4) & 305.09 (123.5) \\
& & & cpl (sd) & 14.08 (6.1) & 11.75 (4.8) & 11.49 (4.7) \\
 &  &HU &MSE (sd) & 499.32 (218.8) & 307.6 (128.7) & 305.09 (123.5) \\
& & & cpl (sd) & 14.08 (6.1) & 11.63 (4.7) & 11.49 (4.7) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 691.55 (503.2) & 193.45 (54.2) & 150.17 (35) \\
& & & cpl (sd) & 12.54 (7.2) & 10.26 (2.7) & 7.81 (1.4) \\
 &  & HU & MSE (sd) & 691.55 (503.2) & 279.21 (117.3) & 150.17 (35) \\
& & & cpl (sd) & 12.54 (7.2) & 13 (4.3) & 7.81 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 282.05 (134.8) & 180.64 (47.6) & 181.49 (48.6) \\
& & & cpl (sd) & 20.37 (6.3) & 13.68 (4) & 14.05 (4) \\
 &  &HU &MSE (sd) & 282.05 (134.8) & 180.84 (47.5) & 181.49 (48.6) \\
& & & cpl (sd) & 20.37 (6.3) & 14.03 (4) & 14.05 (4) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 308.13 (142.9) & 129.39 (19.6) & 122.71 (17.8) \\
& & & cpl (sd) & 22.94 (7.7) & 9.37 (2.1) & 7.91 (1.4) \\
 &  &HU &MSE (sd) & 308.13 (142.9) & 159.14 (30.4) & 122.71 (17.8) \\
& & &cpl (sd) & 22.94 (7.7) & 15.42 (4) & 7.91 (1.4) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U& MSE (sd) & 150.14 (19.7) & 127.48 (14) & 128.21 (15) \\
& & &  cpl (sd) & 25.6 (5.4) & 14.73 (3.8) & 14.73 (3.9) \\
 &  &HU &  MSE (sd) & 150.14 (19.7) & 128.21 (14.9) & 128.21 (15) \\
& & & cpl (sd) & 25.6 (5.4) & 14.7 (3.9) & 14.73 (3.9) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U& MSE (sd) & 157.18 (23.5) & 110.24 (8) & 109.24 (7.8) \\
& & &  cpl (sd) & 30.41 (6.7) & 8.96 (1.3) & 8.3 (1) \\
 &  &HU &  MSE (sd) & 157.18 (23.5) & 123.8 (12.5) & 109.24 (7.8) \\
& & & cpl (sd) & 30.41 (6.7) & 17.18 (3.3) & 8.3 (1) \\
\hline
\end{tabular} 
\caption{Elasticnet (with Elasticnet) combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X_2$.}\label{YX2linenet}
\end{table}

>>>>

	We note $\boldsymbol{\Theta}$ the set of the parameters of the generative model
	\begin{eqnarray}
		P(S|\boldsymbol{X})&\propto& P(\boldsymbol{X}|S)P(S) \label{approxBIC}\\
		-2\log P(\boldsymbol{X}|S)&\approx & BIC=-2\mathcal{L}(\boldsymbol{X},S,\boldsymbol{\Theta})+|\boldsymbol{\Theta}|\log(n)  
	\end{eqnarray}
	But $BIC$ tends to give too complex structures because we test a great range of models. 
	Thus we choose to penalise the complexity a bit more with a hierarchical uniform {\it a priori} law $P(S)=P(I_1 | p_1,I_2,p_2)P(p_1|I_2,p_2)P(I_2|p_2)P(p_2)$  instead of a simple uniform law on $S$ that is generally used and provides no penalty.
%	 Thus we have :
%		\begin{eqnarray}
%		BIC^*(X|S)&=&BIC(X|S) +\ln(P(S)) \label{Bicstar}
%	\end{eqnarray}		
	It increases penalty on complexity for $p_2<\frac{p}{2}$ and $p_1^j<\frac{p}{2}$ . Hence %when using $BIC*$ 
	this constraint on $\hat{p}_2$ and $\hat{p}_1^j$ is made in the MCMC in the followings.
		We do not change $BIC$ but only $P(S)$ so the properties are the same as classical $BIC$ but we will obtain better results when our hypothesis is verified.

@@

\clearpage
\subsection{Results on prediction}
	\subsubsection{$\boldsymbol{Y}$ depends on all variables in $\boldsymbol{X}$}	 \label{tableMSEsimtout}	
We first try the method with a response depending on all covariates (\textsc{CorReg} reduces the dimension and can't give the true model if there is a structure). The datasets used here were those from table \ref{compZvrai}.

@@

$n$ & $p_2$& $P(S)$ & indicator &OLS  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 

@@

\caption{OLS and OLS combined with constrained \textsc{CorReg}. $\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X}$. \textsc{CorReg} logically wins. When $n<p$ the dataset was reduced to $p=n$ automatically by a $QR$ decomposition as the lm function of R does. Without selection, all models have min$(n,p)$ non-zero coefficients.} \label{YXlinOLS}

@@

$n$ & $p_2$&  $P(S)$ &indicator &LASSO  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 

@@

\caption{LASSO (with LAR) combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X}$. \textsc{CorReg} logically wins. LASSO is better than OLS but is improved by \textsc{CorReg} even for large values of $n$.}\label{YXlinLASSO}

@@

$n$ & $p_2$&  $P(S)$&indicator &Elasticnet  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 

@@

\caption{Elasticnet combined with constrained \textsc{CorReg}. $\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X}$. \textsc{CorReg} logically wins. LASSO was better.}\label{YXlinenet}

@@

$n$ & $p_2$&  $P(S)$ &indicator &Stepwise  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 

@@

\caption{Stepwise  combined with constrained \textsc{CorReg}. $\boldsymbol{Y}$ depends on all variables in $\boldsymbol{X}$. \textsc{CorReg} logically wins but stepwise is quite good compared to elasticnet.}\label{YXlinstep}

@@

\clearpage
	\subsubsection{$\boldsymbol{Y}$ depends only on covariates in $\boldsymbol{X_2}$ (worst case for us)}	 \label{tableMSEsimgauche}
We now try the method with a response depending only on variables in $\boldsymbol{X_2}$. The datasets used here were still those from \ref{compZvrai}.
Depending only on $\boldsymbol{X_2}$ imply sparsity and impossibility to obtain the true model when using the true structure. \textsc{CorReg} is still better than classical methods.

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&$P(S)$ &indicator &OLS  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 81781.54 (247281.7) & 507.1 (269.2) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.11 (1) & 25 (0) \\
 &  &HU &MSE (sd) & 81781.54 (247281.7) & 587.07 (425.6) & 593.03 (428.3) \\
& & & cpl (sd) & 30 (0) & 24.82 (0.6) & 25 (0) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 74136.81 (297716.1) & 189.45 (48.1) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 13.85 (0.9) & 9 (0) \\
 &  & HU & MSE (sd) & 74136.81 (297716.1) & 340.53 (169.4) & 144.51 (31.4) \\
& & & cpl (sd) & 30 (0) & 21 (0) & 9 (0) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 684.04 (438.1) & 190.97 (37.7) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.43 (0.7) & 25 (0) \\
 &  &HU &MSE (sd) & 684.04 (438.1) & 196.36 (40.5) & 197.32 (40) \\
& & & cpl (sd) & 41 (0) & 24.99 (0.5) & 25 (0) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 596.32 (323) & 126.94 (15.5) & 119.39 (12.4) \\
& & & cpl (sd) & 41 (0) & 11.45 (0.9) & 9 (0) \\
 &  &HU &MSE (sd) & 596.32 (323) & 168.03 (27.7) & 119.39 (12.4) \\
& & &cpl (sd) & 41 (0) & 21 (0) & 9 (0) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U&  MSE (sd) & 168.35 (20.1) & 133.75 (12.4) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 24.53 (0.7) & 25 (0) \\
 &  &HU &  MSE (sd) & 168.35 (20.1) & 135.04 (13.1) & 135.08 (13.1) \\
& & & cpl (sd) & 41 (0) & 25.01 (0.4) & 25 (0) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U&  MSE (sd) & 168.07 (21.4) & 109.61 (7.4) & 108.64 (7.2) \\
& & &  cpl (sd) & 41 (0) & 10.02 (0.8) & 9 (0) \\
 &  &HU & MSE (sd) & 168.07 (21.4) & 124.23 (11.1) & 108.64 (7.2) \\
& & & cpl (sd) & 41 (0) & 21 (0) & 9 (0) \\
\hline
\end{tabular} 
\caption{OLS and OLS combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X_2}$. Sometimes $\hat{S}$ gives better results than $S$ because $S$ is penalized by the fact that it relies only on covariates not in the true model. } \label{YX2linOLS}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $P(S)$ &indicator &LAR  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 367.45 (198.4) & 298.32 (122.4) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.9 (3.8) & 12.84 (3.8) \\
 &  &HU &MSE (sd) & 367.45 (198.4) & 298.1 (119.1) & 292.53 (102.2) \\
& & & cpl (sd) & 14.37 (5.1) & 12.81 (3.8) & 12.84 (3.8) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 273.12 (267.2) & 166.93 (49) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 8.7 (2.5) & 7.45 (1.4) \\
 &  & HU & MSE (sd) & 273.12 (267.2) & 175.68 (57.5) & 152.45 (39.5) \\
& & & cpl (sd) & 11.7 (5.8) & 9.19 (2.9) & 7.45 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 189.64 (52.5) & 171.97 (45.9) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.4 (2.8) & 13.5 (3.1) \\
 &  &HU &MSE (sd) & 189.64 (52.5) & 174.36 (45.3) & 176.58 (46.8) \\
& & & cpl (sd) & 14.15 (3.9) & 13.57 (3) & 13.5 (3.1) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 163.88 (67.4) & 124.53 (17) & 121.99 (16.6) \\
& & & cpl (sd) & 13.06 (7.2) & 8.29 (1.6) & 7.73 (1.2) \\
 &  &HU &MSE (sd) & 163.88 (67.4) & 133.7 (26.4) & 121.99 (16.6) \\
& & &cpl (sd) & 13.06 (7.2) & 9.65 (3.3) & 7.73 (1.2) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U& MSE (sd) & 129.65 (14.8) & 127.11 (12.1) & 127.46 (12.2) \\
& & &  cpl (sd) & 14.86 (3.1) & 13.97 (2.5) & 14.04 (2.5) \\
 &  &HU &  MSE (sd) & 129.65 (14.8) & 127.46 (12.2) & 127.46 (12.2) \\
& & & cpl (sd) & 14.86 (3.1) & 14.02 (2.5) & 14.04 (2.5) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U&  MSE (sd) & 121.21 (20.1) & 109.66 (7.9) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 8.42 (1.1) & 8.11 (0.8) \\
 &  &HU &  MSE (sd) & 121.21 (20.1) & 112.56 (11.2) & 109.04 (7.8) \\
& & & cpl (sd) & 12.84 (5.2) & 9.77 (2.3) & 8.11 (0.8) \\
\hline
\end{tabular} 
\caption{LASSO (with LAR) combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X_2}$. }\label{YX2linLASSO}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  $P(S)$ &indicator & Elasticnet  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 499.32 (218.8) & 311.41 (137.4) & 305.09 (123.5) \\
& & & cpl (sd) & 14.08 (6.1) & 11.75 (4.8) & 11.49 (4.7) \\
 &  &HU &MSE (sd) & 499.32 (218.8) & 307.6 (128.7) & 305.09 (123.5) \\
& & & cpl (sd) & 14.08 (6.1) & 11.63 (4.7) & 11.49 (4.7) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 691.55 (503.2) & 193.45 (54.2) & 150.17 (35) \\
& & & cpl (sd) & 12.54 (7.2) & 10.26 (2.7) & 7.81 (1.4) \\
 &  & HU & MSE (sd) & 691.55 (503.2) & 279.21 (117.3) & 150.17 (35) \\
& & & cpl (sd) & 12.54 (7.2) & 13 (4.3) & 7.81 (1.4) \\
\hline
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	MSE (sd) & 282.05 (134.8) & 180.64 (47.6) & 181.49 (48.6) \\
& & & cpl (sd) & 20.37 (6.3) & 13.68 (4) & 14.05 (4) \\
 &  &HU &MSE (sd) & 282.05 (134.8) & 180.84 (47.5) & 181.49 (48.6) \\
& & & cpl (sd) & 20.37 (6.3) & 14.03 (4) & 14.05 (4) \\
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&MSE (sd) & 308.13 (142.9) & 129.39 (19.6) & 122.71 (17.8) \\
& & & cpl (sd) & 22.94 (7.7) & 9.37 (2.1) & 7.91 (1.4) \\
 &  &HU &MSE (sd) & 308.13 (142.9) & 159.14 (30.4) & 122.71 (17.8) \\
& & &cpl (sd) & 22.94 (7.7) & 15.42 (4) & 7.91 (1.4) \\
\hline
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U& MSE (sd) & 150.14 (19.7) & 127.48 (14) & 128.21 (15) \\
& & &  cpl (sd) & 25.6 (5.4) & 14.73 (3.8) & 14.73 (3.9) \\
 &  &HU &  MSE (sd) & 150.14 (19.7) & 128.21 (14.9) & 128.21 (15) \\
& & & cpl (sd) & 25.6 (5.4) & 14.7 (3.9) & 14.73 (3.9) \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U& MSE (sd) & 157.18 (23.5) & 110.24 (8) & 109.24 (7.8) \\
& & &  cpl (sd) & 30.41 (6.7) & 8.96 (1.3) & 8.3 (1) \\
 &  &HU &  MSE (sd) & 157.18 (23.5) & 123.8 (12.5) & 109.24 (7.8) \\
& & & cpl (sd) & 30.41 (6.7) & 17.18 (3.3) & 8.3 (1) \\
\hline
\end{tabular} 
\caption{Elasticnet (with Elasticnet) combined with constrained \textsc{CorReg}.$\boldsymbol{Y}$  depends on all variables in $\boldsymbol{X_2}$.}\label{YX2linenet}
\end{table}
